% Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  R.options = list(width = 60)
)
```

# Setup

## Load libraries

```{r}
library(readxl)
library(tidyverse)
library(skimr)
```

## Read data

```{r warning=FALSE}
# Mites data
mites <- read_csv("data/mites.csv")

# Yield and Efficacy data
efficacy <- read_excel("data/efficacy.xlsx")
```

# Exploratory data analysis

## Mites data

```{r}
skim(mites)
```

## Efficacy and Yield data

```{r}
skim(efficacy)
```

## Observations

- Observations were made for 4 weeks.
- Each week, 3 chemicals were tested.
- Each chemical was tested using 3 different concentrations.
- The experiment was designed using 5 replications

```{r}
library(janitor)

# 3 treatments
mites %>% 
   tabyl(Week, Treatment)

# 9 treatments
efficacy %>% 
   tabyl(Treatments)
```

## Data spread

### Mites

**Treatment x Weeks**

```{r}
my_palette <- colorRampPalette(c("forestgreen", "orange", "red"))(n = 299)

ggplot(mites, aes(x = as.factor(Week), y = value)) +
  geom_boxplot(alpha = 0) +
  geom_jitter(aes(colour = value), position = position_jitter(0.2), alpha = 0.5) +
  scale_colour_gradientn(colours = my_palette) +
  labs(x = "Week", y = "Mites", color = "Mites") +
  theme_bw() +
  facet_wrap(Treatment ~ .)
```

**Treatment x Weeks x Concentrations**

```{r}
ggplot(mites, aes(x = as.factor(Week), y = value)) +
  geom_boxplot(alpha = 0) +
  geom_jitter(aes(colour = value), position = position_jitter(0.2), alpha = 0.5) +
  scale_colour_gradientn(colours = my_palette) +
  labs(x = "Week", y = "Mites", color = "Mites") +
  theme_bw() +
  facet_grid(Treatment ~ Conc.)
```

### Efficacy 

```{r}
ggplot(efficacy, aes(x = Treatments, y = Efficacy)) +
  geom_boxplot(alpha = 0) +
  geom_jitter(aes(colour = Efficacy), position = position_jitter(0.2), alpha = 0.5) +
  scale_colour_gradientn(colours = my_palette) +
  labs(x = "Treatment", y = "Efficacy (%)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Yield data 

```{r}
ggplot(efficacy, aes(x = Treatments, y = Honey_Yield)) +
  geom_boxplot(alpha = 0) +
  geom_jitter(aes(colour = Honey_Yield), position = position_jitter(0.2), alpha = 0.5) +
  scale_colour_gradientn(colours = my_palette) +
  labs(x = "Treatment", y = "Honey yield (kg)", color = "Honey yield") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
