% Modeling


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  R.options = list(width = 60)
)
```

# Setup

## Load libraries

```{r}
library(readxl)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(lme4)
library(arm)
library(GAD)
library(lmerTest)
```

## Read data

```{r warning=FALSE}
# Mites data
mites <- read_csv("data/mites.csv")

# Yield and Efficacy data
efficacy <- read_excel("data/efficacy.xlsx")
```

### Indexing Replications

```{r}
mites <- mites %>%
  group_by(Week, Treatment, Conc.) %>%
  mutate(Rep = row_number())
```


# Data analysis

## Three Treatment Groups

### Mortality

-   The data was not normal, so we took natural lag of the mites data.

```{r}
# Model
lme <- lmer(log(value) ~ Treatment + (1|Rep) + (1|Conc.) + (1|Week), data=mites)


# Residuals
library(DHARMa)
simres <- simulateResiduals(lme)
plot(simres)

# ANOVA
anova(lme)
```

**Multiple comparison**

```{r}
library(emmeans)
library(multcomp)

means <- emmeans(lme, pairwise ~ Treatment)
cld(means$emmeans, Letters = LETTERS)
```

**Scott-Knott**

```{r}
library(ScottKnott)
skm <- with(mites,
              SK(x= Treatment,
                 y=log(value),
                 model='y ~ x',
                 which='x'))

skm <- summary(skm)
```


### Efficacy

```{r}
# Model
lme <- lmer(Efficacy ~ Treatment + (1|Replication) + (1|Conc.), data = efficacy)

# Residuals
simres <- simulateResiduals(lme)
plot(simres)

# ANOVA
anova(lme)
```

**Multiple comparison**

```{r}
means <- emmeans(lme, pairwise ~ Treatment)
cld(means$emmeans)
```

**Scott-Knott**

```{r}
ske <- with(efficacy,
              SK(x= Treatment,
                 y=Efficacy,
                 model='y ~ x',
                 which='x'))

ske <- summary(ske)
```

### Honey Yield

```{r}
# Model
lme <- lmer(Honey_Yield ~ Treatment + (1|Replication) + (1|Conc.), data = efficacy)

# Residuals
simres <- simulateResiduals(lme)
plot(simres)

# ANOVA
anova(lme)
```

**Multiple comparison**


```{r}
means <- emmeans(lme, pairwise ~ Treatment)
cld(means$emmeans)
```

**Scott-Knott**

```{r}
sky <- with(efficacy,
              SK(x= Treatment,
                 y=Honey_Yield,
                 model='y ~ x',
                 which='x'))

sky <- summary(sky)
```


## Nine Treatment Groups

### Mortality

```{r}
# Model
lme <- lmer(log(value) ~ Treatments + (1|Rep) + (1|Conc.) + (1|Week), data=mites)


# Residuals
simres <- simulateResiduals(lme)
plot(simres)

# ANOVA
anova(lme)
```

**Multiple comparison**

```{r}
means <- emmeans(lme, pairwise ~ Treatments)
cld(means$emmeans, Letters = LETTERS)
```

**Scott-Knott**

```{r}
skm <- with(mites,
              SK(x= Treatments,
                 y=log(value),
                 model='y ~ x',
                 which='x'))

skm <- summary(skm)
```

### Efficacy

```{r}
# Model
lme <- lmer(Efficacy ~ Treatments + (1|Replication) + (1|Conc.), data = efficacy)

# Residuals
simres <- simulateResiduals(lme)
plot(simres)

# ANOVA
anova(lme)
```

**Multiple comparison**

```{r}
means <- emmeans(lme, pairwise ~ Treatments)
cld(means$emmeans)
```

**Scott-Knott**

```{r}
ske <- with(efficacy,
              SK(x = Treatments,
                 y = Efficacy,
                 model='y ~ x',
                 which='x'))

ske <- summary(ske)
```

### Honey Yield

```{r}
# Model
lme <- lmer(Honey_Yield ~ Treatments + (1|Replication) + (1|Conc.), data = efficacy)

# Residuals
simres <- simulateResiduals(lme)
plot(simres)

# ANOVA
anova(lme)
```

**Multiple comparison**

```{r}
means <- emmeans(lme, pairwise ~ Treatments)
cld(means$emmeans)
```

**Scott-Knott**

```{r}
sky <- with(efficacy,
              SK(x= Treatments,
                 y=Honey_Yield,
                 model='y ~ x',
                 which='x'))

sky <- summary(sky)
```
